%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_06.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_06.tex 51 2024-01-04 03:07:16Z KneadProject $}

\chapter{Operational scenarios}
\label{chap:Operational scenarios}
\input{DIDINFO_Snippets/OCD/OCD_6.0_DIDINFO.tex}

This chapter describes different scenarios in which the \ThisSystem is to be used.


\section{Use Case 1: Low Water Sensor}
\label{loc:UseCase1}
\input{DIDINFO_Snippets/OCD/OCD_6.1_DIDINFO.tex}

One of the most important uses of this system is to monitor water level. When the water level is low the Rancillio Silvia V2
could damage itself. Providing the user with two states Full and empty. When the system has water it is considered in the full
state. The system should operate as normal. When the water level is low the system must report this to the user using the Built
in screen. The system should also lock the user out of other functionality.

\section{Use Case 2: Pulling an Espresso Shot}
\label{loc:UseCase2}
%\input{DIDINFO_Snippets/OCD/OCD_6.1_DIDINFO.tex}

When the user wants to pull a shot the user should prepare their espresso as they usually do. Measuring the weight 
of ground coffee in their portafilter. Once this measurement is received and the shot is ready to pull. The user should place
their cup in the brew area. Then the user should input their coffee weight into the \ThisSystem using the user interface.
The pumps will engage and the espresso will be brewed. The system will monitor the weight of liquid that falls into the cup,
when the desired brew weight is reached the pumps will disengage and system will summarize the shot to the user and return
to a ready state waiting for the next shot.

\section{Use Case 3: Reviewing a Shot}
\label{loc:UseCase3}

The system will allow the user to review previous reviewed shots. This information will include time and weight and well
as some metrics around how the shot was pulled. This will be done by \TBD


\section{Use Case 4}
\label{loc:UseCase3}

This section is \TBD.