%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_04.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_04.tex 51 2024-01-04 03:07:16Z KneadProject $}


\chapter{Justification for and nature of changes}
\label{chap:Justification for and nature of changes}
\input{DIDINFO_Snippets/OCD/OCD_4.0_DIDINFO.tex}

This is the first formal release for the \ThisSystem, the justification for these changes are to release an initial product.
This product meets a user's need and therefor should be created.

\section{Justification for change}
\label{sec:Justification for change}
\input{DIDINFO_Snippets/OCD/OCD_4.1_DIDINFO.tex}

The \ThisSystem provides a service to all levels of users that are interested in espresso. It gives them the ability
to refine and record their process.  

\section{Description of needed changes}
\label{sec:Description of needed changes}
\input{DIDINFO_Snippets/OCD/OCD_4.2_DIDINFO.tex}

Espresso is a complicated coffee. It has many factors that impact taste. \ThisSystem serves to simplify these variables
through automation. Specifically monitoring Time to Brew Ratio.


\section{Priorities among the changes}
\label{sec:Priorities among the changes}
\input{DIDINFO_Snippets/OCD/OCD_4.3_DIDINFO.tex}

The \ThisSystem prioritizes the following
\begin{itemize}
 \item Easy of use
 \item Information should be easily displayed to the user
 \item Information should be easily changed by the user
 \item System will turn on and off pumps
 \item System will monitor water tank to prevent boiler running with no water
\end{itemize}

\section{Changes considered but not included}
\label{sec:Changes considered but not included}
\input{DIDINFO_Snippets/OCD/OCD_4.4_DIDINFO.tex}

The \ThisSystem will be considering ways to easily present information from previous shots. This may include
a web interface or additional system to record and present historical data. This may also allow the user to 
rate their shots in order to remember and catalog their espresso.


\section{Assumptions and constraints}
\label{sec:Assumptions and constraints}
\input{DIDINFO_Snippets/OCD/OCD_4.5_DIDINFO.tex}

It is assumed that a user has some experience with espresso, or the desire to learn. This system will not
teach a user and will not fix user errors.
