%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_05.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_05.tex 51 2024-01-04 03:07:16Z KneadProject $}


\chapter{Concept for a new or modified system}
\label{chap:Concept for a new or modified system}
\input{DIDINFO_Snippets/OCD/OCD_5.0_DIDINFO.tex}

This chapter summaries the problem that is to be addressed by the \ThisSystem. This is the initial release
and it is here to address as many problems as possible with a quick time to market.


\section{Background, objectives, and scope}
\label{sec:Background, objectives, and scope}
\input{DIDINFO_Snippets/OCD/OCD_5.1_DIDINFO.tex}

This system primary goal is to automate espresso extraction to improve ease of use for new users. As well
as improving consistency and giving users additional data to improve espresso extraction.


\section{Operational policies and constraints}
\label{sec:Operational policies and constraints}
\input{DIDINFO_Snippets/OCD/OCD_5.2_DIDINFO.tex}

This section is \TBD.


\section{Description of the new or modified system}
\label{sec:Description of the new or modified system}
\input{DIDINFO_Snippets/OCD/OCD_5.3_DIDINFO.tex}

The \ThisSystem is designed to be installed inside a Rancillio Silvia V2 espresso machine. The rest is \TBD.


\section{Users/affected personnel}
\label{sec:Users/affected personnel}
\input{DIDINFO_Snippets/OCD/OCD_5.4_DIDINFO.tex}

An experienced coffee enthusiasts gains the convince of automation in their process and the accuracy an automated system
provides allowing for more consistent espresso shots. In addition the monitoring of shot data allows additional Information
for the user to tweak in order to perfect their espresso.

A new user may not have the know how to pull their own shots. The automation provides a simple and effective interface
to get the user pulling the right ratio of coffee to water. In addition the \ThisSystem provides basic feedback to 
let the user know if they may have an under or over extracted espresso. This system aims to reduce variables to allow for
repeatable and consistent espresso without months or years of training.



\section{Support concept}
\label{sec:Support concept}
\input{DIDINFO_Snippets/OCD/OCD_5.5_DIDINFO.tex}

This section is \TBD.

