%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20OCD/OCD_Chapter_07.tex $}
{$LastChangedDate: 2024-01-03 22:07:16 -0500 (Wed, 03 Jan 2024) $}
{$LastChangedRevision: 51 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: OCD_Chapter_07.tex 51 2024-01-04 03:07:16Z KneadProject $}

\chapter{Summary of impacts}
\label{chap:Summary of impacts}
\input{DIDINFO_Snippets/OCD/OCD_7.0_DIDINFO.tex}

This chapter summarizes the impact of \ThisSystem.


\section{Operational impacts}
\label{sec:Operational impacts}
\input{DIDINFO_Snippets/OCD/OCD_7.1_DIDINFO.tex}

The \ThisSystem improves consistency, easy of use, and adds system monitoring to an existing system. The improved 
efficiency and ease of use should improve users satisfaction with the system.


\section{Organizational impacts}
\label{sec:Organizational impacts}
\input{DIDINFO_Snippets/OCD/OCD_7.2_DIDINFO.tex}

This system is designed to be used in home environment and focuses on individual user satisfaction. This system should
improve the users experience. Decreasing the chance of damaging the Rancillio Silvia system. In addition to repeatability
and ease of use with pulling espresso shots.


\section{Impacts during development}
\label{sec:Impacts during development}
\input{DIDINFO_Snippets/OCD/OCD_7.3_DIDINFO.tex}

The development of this system is impacted by accessibility to the Rancillio Silvia machine. Development will be done
in the C language and run on the ESP32 microcontroller. This system will require access to coffee in order to accurately
develop the system.