\ref{rqt:LightSingleMode} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The system shall be capable of Single Mode Broadcast.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSingleMode} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of Single Mode Broadcast.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumMultiMode} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of Multi-Mode Broadcast.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSubStateFMAndSMS} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of simultaneously broadcasting both FM radio signals and SMS dissemination.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSubStateFMAndAM} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of simultaneously broadcasting both FM and AM radio signals.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSubStateFMAndTV} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of simultaneously broadcasting FM radio and TV signals.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSubStateFMAndSW} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of simultaneously broadcasting FM and SW radio signals.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavySingleMode} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of Single Mode Broadcast.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavyMultiMode} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of Multi-Mode Broadcast.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavySubStateFMAndSMS} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of simultaneously broadcasting both FM radio signals and SMS dissemination.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavySubStateFMAndAM} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of simultaneously broadcasting both FM and AM radio signals.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavySubStateFMAndTV} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of simultaneously broadcasting FM radio and TV signals.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavySubStateFMAndSW} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of simultaneously broadcasting FM and SW radio signals.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:GUI} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall provide a user interface as defined in the \ThisSys \SUM.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Command Line} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall have a command line environment for authorized users to access the operating system architecture.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Media Sources} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be capable of manually ingesting media from different sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Media IP Stream} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be capable of receiving and processing a pre-encoded IP stream.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Radio Rebroadcast} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be capable of receiving an FM radio program and storing the content for later rebroadcasting.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium AM Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium AM External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall maintain \AM broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy AM Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy AM External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall maintain \AM broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium SW Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium SW External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall maintain \SW broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy SW Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy SW External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall maintain \SW broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:FM Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:FM External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall maintain FM broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium VHF Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium VHF External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall maintain \VHF broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy VHF Self Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy VHF External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall maintain \VHF broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:UHF Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall not generate detrimental out-of-band interference in the adjacent channels or frequency bands nor create detrimental conducted radiation.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:UHF External Interference} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall maintain \UHF broadcast operation in the presence of interference generated by external sources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Control Remote Device} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The system operator shall be able to control the system broadcasts using a device with a wired or wireless connection at a standoff distance of at least 100m.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium Prop Model} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall visually depict the RF propagation on a device.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy Prop Model} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall visually depict the RF propagation on a device.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:BIT Operational Status} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall run a self-test at startup and include a visual indicator of its operational status.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:BIT Logs} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be able to store and export \BIT logs in .txt and .csv formats.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:IDR_Data_Storage} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall store digital files received for transmission using 2 TB of internal storage.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:IDR_Info_Transport} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be able to manually upload and download digital files using external SD card, CD, and DVD formats.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:IDR_Report_Logs} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The system shall locally store reports for up to 12 months and be capable of exporting in .txt, .csv, and .xml formats.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Temperature} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be tested to meet applicable environmental standards as outlined in Military Standard 810G (MIL-STD-810G).\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Shock} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall withstand the effects of shock (Transit Drop) per Military Standard 810H (MIL-STD-810H), Method 516.6, Procedure IV.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Vibration} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall withstand the effects of vibration (General) per Military Standard 810H (MIL-STD-810H), Method 514.6, Procedures I and III.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:LightSpace} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be modular and packaged for transport into 2 ruggedized cases.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSpace} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be modular and packaged for transport into 10 ruggedized cases.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:LightSystemWeight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The complete BDP-Light system shall weigh no more than 100 pounds.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:LightCoreWeight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light core system shall weigh no more than 10 pounds.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumSystemWeight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The complete BDP-Medium system shall weigh no more than 500 pounds.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumCoreWeight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium core system shall weigh no more than 65 pounds.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavySystemWeight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The complete BDP-Heavy system shall weigh no more than 2000 pounds.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavyCoreWeight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy core system shall weigh no more than 65 pounds.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:LightInternalPower} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be capable of operating on an internal military standard radio battery.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:LightExternalPower} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be able to connect to external 120/240 \VAC, 50/60 Hz power.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:MediumExternalPower} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of connecting to a 3 kW generator producing 120/240 \VAC, 50/60 Hz power.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:HeavyExternalPower} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of connecting to a 10 kW generator producing 120/240 \VAC, 50/60 Hz power.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:EM} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants will conform to the electromagnetic environmental effects requirements as documented in DOD Directive 3222.3.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Light Duty Cycle} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be capable of continuously transmitting for 8 hours per day for 30 consecutive days.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Medium Duty Cycle} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of continuously transmitting for 18 hours per day for 30 consecutive days.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Heavy Duty Cycle} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of continuously transmitting for 18 hours per day for 30 consecutive days.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:DesignDefences_SystemSetUpHeavy} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be capable of being set up in one (1) hour with five (5) soldiers.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:DesignDefences_SystemSetUpMedium} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be capable of being set up in one (1) hour with five (5) soldiers.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:DesignDefences_SystemSetUpLight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be capable of being set up in thirty (30) minutes with three (3) soldiers.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:DesignDefences_MastHeavy} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Heavy system shall be erectable by a five (5) person team.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:DesignDefences_MastMedium} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be erectable by a five (5) person team.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:DesignDefences_MastLight} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be erectable by a three (3) person team.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Transportability} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall be transportable by air, ground, and maritime resources.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Transit Cases Light} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Light system shall be configured in ruggedized transit cases, not to exceed 2-man lift in accordance with Military Standard 1472G (MIL-STD-1472G) and meet commercial airline size and dimension requirements for checked baggage (Domestic and International travel).\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:Transit Cases Medium} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}The BDP-Medium system shall be configured in ruggedized transit cases, not to exceed 2-man lift in accordance with Military Standard 1472G (MIL-STD-1472G) and meet commercial airline size and dimension requirements for checked baggage (Domestic and International travel).\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:PlaylistManager} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants shall interface with an approved external broadcast playlist manager that will provide the operator the ability to manage programming in real-time.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
\ref{rqt:PlaylistLength} & \begin{minipage}{\KsaRightColumnWidth}{\vspace{\KsaVspace}All BDP system variants' playlists shall have continuous broadcast programming with a pause, resume, repeat, and schedule/timer functions, and a minimum time block of four (4) hours.\vspace{\KsaVspace}}\end{minipage}\\ \hline%
