%%% SVN stuff
\svnidlong
{$HeadURL: https://svn.riouxsvn.com/kneadlatxinputs/ExampleArtifactFolders/0%20-%20SDP/SDP_Chapter_04.tex $}
{$LastChangedDate: 2023-12-24 20:45:24 -0500 (Sun, 24 Dec 2023) $}
{$LastChangedRevision: 27 $}
{$LastChangedBy: KneadProject $}
\svnid{$Id: SDP_Chapter_04.tex 27 2023-12-25 01:45:24Z KneadProject $}


\chapter{System Development Plans}
\label{loc:PlansForSystemDevelopment}
\input{DIDINFO_Snippets/SDP/SDP_4.0.0_DIDINFO.tex}

This chapter highlights the development plan for different portions of the \system design.  \TBD.

\section{Hardware Development Plans}
\label{loc:SDP_HardwareDevelopmentPlans}
\input{DIDINFO_Snippets/SDP/SDP_4.1.0_DIDINFO.tex}

This system will interface with a Rancillio Silvia V2 Espresso Machine. This will require access to the inside parts of this machine.
This hardware will be tested in steps. Focusing on individual parts, confirming functionality with reference designs or basic manual functionality.
This hardware must interface with the existing Espresso Machine. This will require wiring into AC circuits and building or attaching parts into the mechanical 
features that already exist.

\section{Firmware Development Plans}
\label{loc:SDP_FirmwareDevelopmentPlans}
\input{DIDINFO_Snippets/SDP/SDP_4.2.0_DIDINFO.tex}

Firmware will be developed in parts with unit level tests for each piece that is added. Common libraries will be targeted to accelerate development.
All new firmware should be tested as it is developed. The specifics of this code are \TBD.

\section{Software Development Plans}
\label{loc:SDP_SoftwareDevelopmentPlans}
\input{DIDINFO_Snippets/SDP/SDP_4.3.0_DIDINFO.tex}

This section will focus on the network design and is \TBD.


\section{Integration Plans}
\label{loc:SDP_IntegrationPlans}
\input{DIDINFO_Snippets/SDP/SDP_4.4.0_DIDINFO.tex}

This section will discus the requirements for the hardware and software to interface with the existing hardware as well as the firmware and software communication. \TBD.


\section{Testing Plans}
\label{loc:SDP_TestingPlans}
\input{DIDINFO_Snippets/SDP/SDP_4.5.0_DIDINFO.tex}

This system will be tested with the development of unit tests and control testing. Specifics are \TBD

\section{Other Development Activities}
\label{loc:SDP_OtherDevelopmentActivities}
\input{DIDINFO_Snippets/SDP/SDP_4.6.0_DIDINFO.tex}

This section is \TBD.