
A summary of the modes is provided in Table~\ref{tab:Modes}.
This table also provides a list of the sub-states in which each mode is valid.
See the formal specifications, if applicable, in the following sections for formal statement of the mode requirements, and accompanying notes that provide further clarification on the meanings of the states.
\begin{table}[htbp]
	\begin{center}
		\begin{tabular}{|p{1.0in}|p{4.0in}|p{1.0in}|}
			\hline
			\hline
			     \multicolumn{3}{|c|}{{\bf MODES}}\\
			\hline
{\bf Name} & {\bf Summary}	& {\bf Valid Sub-States}\\
			\hline
			\hline
Default Mode & Default Mode & With Water \\ \hline
Low-Water-Mode C & Low Water Mode & Without Water \\ 
			\hline
			\hline
			\end{tabular}
				\caption{Summary of Modes for \ThisSystem}
				\label{tab:Modes}
		\end{center}
\end{table}

%%%
%%% include subsections and/or files with requirements for the sub-states as needed
%%%

%%% \ONERQMTV[9] is macro for consistently formatted requirements
\ONERQMTV
% #1 is requirement Number
{\RqtNumberBase.1}
% #2 is Title
{Default Mode}
% #3 is requirement label (expected to be of form rqt:XXX)
{rqt:ModeOne}
% #4 is Text of the specification
{The system shall provide the Mode-1 mode.}
% #5 is Status (S in {(T), (O), (I), (D)} listed by phase as \item [] S)
{
	\item [Phase 1] Threshold
}
% #6 is Acceptance
{This requirement shall be verified by demonstration.}
% #7 is Traceability
{
	\item [N/A] This requirement is a base requirement.
}
% #8 is Notes; listed as enumeration \item ...
{
	\item The Default mode generalizes the case where the system is operational
	\item The system should be able to take user input to control the system
}
% #9 is changebar version
{P1}
%%%%% end \ONERQMTV[9] macro


%%% \ONERQMTV[9] is macro for consistently formatted requirements
\ONERQMTV
% #1 is requirement Number
{\RqtNumberBase.2}
% #2 is Title
{Without Water Mode}
% #3 is requirement label (expected to be of form rqt:XXX)
{rqt:ModeTwo}
% #4 is Text of the specification
{The system shall provide the Without Water mode.}
% #5 is Status (S in {(T), (O), (I), (D)} listed by phase as \item [] S)
{
	\item [Phase 1] Threshold
}
% #6 is Acceptance
{This requirement shall be verified by demonstration.}
% #7 is Traceability
{
	\item [N/A] This requirement is a base requirement.
}
% #8 is Notes; listed as enumeration \item ...
{
	\item The Without Water mode generalizes the case where the system is out of water
	\item The system should not take user input and prompt them to fill the system
}
% #9 is changebar version
{P1}
%%%%% end \ONERQMTV[9] macro
